Visualizations for the manuscript

### 2022-10-17 metanalysis_visualization/manuscript_Figures.Rmd
removing redundant data frame: all_icd_all

Put all the aggregated counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  print(outputFiles[i])
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
    count_icd_all <- count_icd
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
    length_hospitalisation_values_all <- length_hospitalisation_values
    mental_codes_qc_output_all <- mental_codes_qc_output %>%
      select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    table1_all <- table1
  } else {
    count_icd_all <- rbind(count_icd_all, count_icd)
    perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
    patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc)
    mental_codes_qc_output_all <- rbind( mental_codes_qc_output_all,
                                         mental_codes_qc_output %>%
                                           select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    )
    table1_all <- rbind( table1_all, table1)
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
    length_hospitalisation_values_all <- tryCatch(
      rbind(length_hospitalisation_values_all, length_hospitalisation_values),
      error = function(e) length_hospitalisation_values_all
    )
    rm(count_icd,patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
       perc_disorder_group,ratios_patients_with_without_psy,
       patient_count_psy_period_psy_clear, mental_codes_qc_output, table1, length_hospitalisation_values)
  }
}

@@

count_icd_all <- filter_by_dates(count_icd_all, start_date_plots, end_date_plots)
patient_count_psy_period_psy_all <- filter_by_dates(patient_count_psy_period_psy_all, start_date_plots, end_date_plots)
patients_hospitalized_agg_sex_perc_all <- filter_by_dates(patients_hospitalized_agg_sex_perc_all, start_date_plots, end_date_plots)
perc_disorder_group_all <- filter_by_dates(perc_disorder_group_all, start_date_plots, end_date_plots)
ratios_patients_with_without_psy_all <- filter_by_dates(ratios_patients_with_without_psy_all, start_date_plots, end_date_plots)
```

@@

```{r}
count_icd_all <- left_join(count_icd_all, country_map, on = "site_id")
patient_count_psy_period_psy_all <- left_join(patient_count_psy_period_psy_all, country_map, on = "site_id")
patients_hospitalized_agg_sex_perc_all <- left_join(patients_hospitalized_agg_sex_perc_all, country_map, on = "site_id")
perc_disorder_group_all <- left_join(perc_disorder_group_all, country_map, on = "site_id")
ratios_patients_with_without_psy_all <- left_join(ratios_patients_with_without_psy_all, country_map, on = "site_id")

@@

```{r}
median_table1_all <- length_hospitalisation_values_all %>% 
  group_by(period) %>% 
  summarise(median_hospitalisation = paste0(median(len_hospitalisation), " (", IQR(len_hospitalisation), ")")) %>% 
  pivot_wider(names_from = period, values_from = median_hospitalisation) %>% 
  mutate(Category = "Length of stays", 
         name = "median") %>% 
  select(Category, name, before_pandemic, during_pandemic) %>% 
  rename(before_pandemic_count = before_pandemic, 
         during_pandemic_count = during_pandemic)
median_table1_all$before_pandemic_count <- as.character(median_table1_all$before_pandemic_count)
median_table1_all$during_pandemic_count <- as.character(median_table1_all$during_pandemic_count)

mean_table1_all <- length_hospitalisation_values_all %>% 
  group_by(period) %>% 
  summarise(mean_hospitalisation = round( mean(len_hospitalisation), 2), 
            conf_interval = gmodels::ci( len_hospitalisation ), 
            ci_length = paste0("[", round(as.numeric(conf_interval[2]), 2), " , ",  round(as.numeric(conf_interval[3]),2), "]")) %>%
  mutate(mean_hospitalisation = paste0(as.character(mean_hospitalisation), as.character(ci_length))) %>% 
  select(period, mean_hospitalisation) %>%
  unique() %>%
  pivot_wider(names_from = period, values_from = mean_hospitalisation) %>% 
  mutate(Category = "Length of stays", 
         name = "mean [95% CI]") %>% 
  select(Category, name, before_pandemic, during_pandemic) %>% 
  rename(before_pandemic_count = before_pandemic, 
         during_pandemic_count = during_pandemic)
```

@@

```{r}
# Get count_icd_all in the same format that patient_count_psy_period_psy_all, because first n last months missing ... 
count_icd_all_boot <- count_icd_all %>% 
  group_by(siteid) %>% # necessary to generate time correctly 
  rename(percentage = percentage_psy) %>% 
  mutate(month_year = format(time_p, "%m"),
         time = seq_along(time_p))

bootstrapped <- count_icd_all_boot %>%
  group_by(siteid) %>% 
  group_map( ~bootstrapping_slopes(.x, group_name = .y, bootstrap_size = bootstrap_size))
names(bootstrapped) <- unique(count_icd_all_boot$siteid)

@@

quantile_bootstrapped_fitted_all <- bootstrapped_fitted_all %>%
  group_by(time_p, period, siteid) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles") %>% 
  left_join(country_map, by = "siteid")

@@

```{r}
pvalues_boot_complete <- pvalues_boot %>% 
  inner_join(ci_boot) %>% 
  inner_join(country_map) %>% 
  arrange(plotsLabel) %>% 
  #mutate(string = paste0(observed_slope_coefficient, "% ", ci, " (p-value ", format.pval(pvalue, digits = 3, eps = 10**-2), ")")) %>%
  mutate(string = paste0(observed_slope_coefficient, "% ", ci)) %>%
  select(plotsLabel, string) %>% 
  pivot_wider(names_from = term, values_from = string) %>% 
  select(plotsLabel, before_slope, during_slope, difference_slope) %>% 
  rename("Before pandemic trend [95% CI] (p-value)" = before_slope,
        "Since pandemic trend [95% CI] (p-value)" = during_slope,
        "Difference before/since pandemic trend [95% CI] (p-value)" = difference_slope)

@@

```{r}
#plot_annotations_df_primary <- pvalues_boot %>%
#  select(siteid, label) %>% 
#  filter(term == "difference_slope") %>% 
#  left_join(country_map)

plot_annotations_df_primary <- pvalues_boot_complete %>%
  select( siteid, label = `Difference before/since pandemic trend [95% CI] (p-value)`, plotsLabel )%>% 
  left_join(country_map)

@@

```{r}
# Get count_icd_all in the same format that patient_count_psy_period_psy_all, because first n last months missing ...

@@

counts <- count_icd_all %>%
  mutate( time = seq_along(time_p),
         month_year = format(time_p, "%m")) %>%
  select( plotsLabel, time_p, time, month_year, count_psy_patients = count_psy, total_cases = count_icd )

>>>>

Put all the aggregated counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  print(outputFiles[i])
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
    length_hospitalisation_values_all <- length_hospitalisation_values
    mental_codes_qc_output_all <- mental_codes_qc_output %>%
      select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    table1_all <- table1
  } else {
    perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
    patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc)
    mental_codes_qc_output_all <- rbind( mental_codes_qc_output_all,
                                         mental_codes_qc_output %>%
                                           select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    )
    table1_all <- rbind( table1_all, table1)
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
    length_hospitalisation_values_all <- tryCatch(
      rbind(length_hospitalisation_values_all, length_hospitalisation_values),
      error = function(e) length_hospitalisation_values_all
    )
    rm(patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
       perc_disorder_group,ratios_patients_with_without_psy,
       patient_count_psy_period_psy_clear, mental_codes_qc_output, table1, length_hospitalisation_values)
  }
}

@@

patient_count_psy_period_psy_all <- filter_by_dates(patient_count_psy_period_psy_all, start_date_plots, end_date_plots)
patients_hospitalized_agg_sex_perc_all <- filter_by_dates(patients_hospitalized_agg_sex_perc_all, start_date_plots, end_date_plots)
perc_disorder_group_all <- filter_by_dates(perc_disorder_group_all, start_date_plots, end_date_plots)
ratios_patients_with_without_psy_all <- filter_by_dates(ratios_patients_with_without_psy_all, start_date_plots, end_date_plots)
```

```{r}
patient_count_psy_period_psy_all <- patient_count_psy_period_psy_all %>% 
  mutate(count_icd = count_no_psy_patients + count_psy_patients)

@@

```{r}
patient_count_psy_period_psy_all <- left_join(patient_count_psy_period_psy_all, country_map, on = "site_id")
patients_hospitalized_agg_sex_perc_all <- left_join(patients_hospitalized_agg_sex_perc_all, country_map, on = "site_id")
perc_disorder_group_all <- left_join(perc_disorder_group_all, country_map, on = "site_id")
ratios_patients_with_without_psy_all <- left_join(ratios_patients_with_without_psy_all, country_map, on = "site_id")

@@

```{r}
median_table1_all <- length_hospitalisation_values_all %>% 
  group_by(period) %>% 
  summarise(median_hospitalisation = paste0(median(len_hospitalisation),
                                            " (",
                                            IQR(len_hospitalisation), ")"), 
            .groups = "drop") %>% 
  pivot_wider(names_from = period, values_from = median_hospitalisation) %>% 
  mutate(Category = "Length of stays", 
         name = "median") %>% 
  select(Category, name, before_pandemic, during_pandemic) %>% 
  rename(before_pandemic_count = before_pandemic, 
         during_pandemic_count = during_pandemic)
median_table1_all$before_pandemic_count <- as.character(median_table1_all$before_pandemic_count)
median_table1_all$during_pandemic_count <- as.character(median_table1_all$during_pandemic_count)

mean_table1_all <- length_hospitalisation_values_all %>% 
  group_by(period) %>% 
  summarise(mean_hospitalisation = round( mean(len_hospitalisation), 2), 
            conf_interval = gmodels::ci( len_hospitalisation), 
            ci_length = paste0("[", round(as.numeric(conf_interval[2]), 2),
                               " , ",
                               round(as.numeric(conf_interval[3]),2), "]"), 
            .groups = "drop"
            ) %>%
  mutate(mean_hospitalisation = paste0(as.character(mean_hospitalisation), as.character(ci_length))) %>% 
  select(period, mean_hospitalisation) %>%
  unique() %>%
  pivot_wider(names_from = period, values_from = mean_hospitalisation) %>% 
  mutate(Category = "Length of stays", 
         name = "mean [95% CI]") %>% 
  select(Category, name, before_pandemic, during_pandemic) %>% 
  rename(before_pandemic_count = before_pandemic, 
         during_pandemic_count = during_pandemic)
```

@@

```{r}

bootstrapped <- patient_count_psy_period_psy_all %>%
  group_by(siteid) %>% 
  group_map( ~bootstrapping_slopes(.x, group_name = .y, bootstrap_size = bootstrap_size))
names(bootstrapped) <- unique(patient_count_psy_period_psy_all$siteid)

@@

quantile_bootstrapped_fitted_all <- bootstrapped_fitted_all %>%
  group_by(time_p, time, period, siteid) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975), 
            .groups = "drop") %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles") %>% 
  left_join(country_map, by = "siteid")

@@

```{r}
pvalues_boot_complete <- pvalues_boot %>% 
  inner_join(ci_boot, by = c("siteid", "term")) %>% 
  inner_join(country_map, by = c("siteid")) %>% 
  arrange(plotsLabel) %>% 
  #mutate(string = paste0(observed_slope_coefficient, "% ", ci, " (p-value ", format.pval(pvalue, digits = 3, eps = 10**-2), ")")) %>%
  mutate(string = paste0(observed_slope_coefficient, "% ", ci)) %>%
  select(siteid, term, plotsLabel, string) %>% 
  pivot_wider(names_from = term, values_from = string) %>% 
  select(siteid, plotsLabel, before_slope, during_slope, difference_slope) %>% 
  rename("Before pandemic trend [95% CI] (p-value)" = before_slope,
        "Since pandemic trend [95% CI] (p-value)" = during_slope,
        "Difference before/since pandemic trend [95% CI] (p-value)" = difference_slope)

@@

```{r}
plot_annotations_df_primary <- pvalues_boot_complete %>%
  select( siteid, label = `Difference before/since pandemic trend [95% CI] (p-value)`, plotsLabel )%>% 
  left_join(country_map, by = c("siteid", "plotsLabel"))
```

```{r, fig.width = 20, fig.height=14}
bootstrapped_fitted_all %>%
  # mutate( time = time + 0.5) %>%

          # 
          # ),
          # time_p = as.character(time_p),
          #         time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
          #         time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
          #         time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
          #         time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
          #         time_p = as.Date(time_p))%>%
  ggplot(aes(x = time, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("plotsLabel", scales = "free_y", labeller = label_wrap_gen(width = 35,multi_line = TRUE), ncol = 2) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            # %>% mutate(time_p = as.Date(time_p)+ 15,  time_p = as.character(time_p),
            #       time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
            #       time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
            #       time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
            #       time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
            #       time_p = as.Date(time_p)),
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  # geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ] 
  #           %>% mutate(time_p = as.Date(time_p)+ 15, 
  #                      time_p = as.character(time_p),
  #                 time_p = if_else(time_p == '2020-04-16', as.character('2020-04-01'), time_p), 
  #                 time_p = if_else(time_p == '2020-03-16', as.character('2020-03-31'), time_p),
  #                 time_p = if_else(time_p == '2021-04-16', as.character('2021-04-30'), time_p),
  #                 time_p = if_else(time_p == '2019-02-16', as.character('2019-02-01'), time_p),
  #                 time_p = as.Date(time_p)),
  #           aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             # %>% mutate( time_p = as.Date(time_p)+ 15),
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_x_continuous(breaks = scales::breaks_width(1, offset = 0)) + 
  geom_vline(xintercept = as.Date("2020-04-01"), linetype = 6)+
  scale_x_date(breaks = "1 month", labels=date_format("%b %Y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_df_primary, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(
    #title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
    #subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 14),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x =element_blank(),
        axis.title.y = element_text(size = 8),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic"), 
        legend.position="bottom")

# ggsave("figure1_boostrapped_all.png", height = 20, width = 25, units = "cm")
```

@@

```{r}

@@

counts <- patient_count_psy_period_psy_all %>%
  select( plotsLabel, time_p, time, month_year, count_psy_patients, total_cases = count_icd )
